Some Nice Title Goes Here, Eventually\ldots

### 2014-08-31 doc/tacs2014/article.tex
Added kanji example (yama, ryuu, kane) to illustrate the variance in complexity.
Stroke categories, stroke number histogram, previous work progress

	This paper documents a work in progress on the topic intelligent handwriting recognition of Japanese characters.
	The remainder of the article is structured as follows:
	In section \ref{sec:problem_description} we present the Japanese writing system and outline the primary issues with handwriting recognition for asian script;
	thereafter in \ref{sec:previous_work}, we discuss some notable advances aimed at solving various aspects of the aforementioned problems.
	An explanation of the proposed solution is given in section \ref{sec:proposed_solution}, and an initial, experimental implementation is described in \ref{sec:experiments}
	-- the results of which are recorded and examined in section \ref{sec:experiment_results}. Finally, conclusions and future work is presented in sections
	\ref{sec:conclusions} and \ref{sec:future_work}, respectively.

@@

	Any form of digital handwriting recognition is a complex undertaking,
	where the performance of the system is impacted by a multitude of factors -- spanning
	everything from the quality and quantity of training data, to resilience toward input
	translation, rotation, and noise. As the number of candidate categories increases
	the size of the search space, however, the task quickly grows monumental.

@@

	Given that the category search space for Japanese characters is an order of magnitude larger than its western counterparts,
	and that other characteristics must be taken into account, it becomes apparent that the same designs that
	yields highly accurate results on the latin alphabet will not perform satisfactory when applied to asian character recognition \cite{tappert1990state, liu2004online}
	-- unless it relies on complex, computationally expensive techniques such as for instance ``deep'' neural networks. \cite{ciresan2012multi}

	In continuation, we describe a flexble, modular design scheme that splits the identification task into coarse and fine steps,
	thereby reducing the complexity of each undertaking. The design scheme also permits replacing classification strategies,
	and facilitates the parallelization of network training.

@@

	Testing a cite \cite{zhu2014robust}.

	\ldots

	In \cite{nakai2001substroke}, the authors adapt a continuous speech recognition algorithm utilizing
	hidden Markov models for the purpose of online kanji recognition. By identifying and classifying
	substrokes, which in turn are employed as search keys in a character dictionary, this approach vastly
	reduced the memory requirements for both their models and their dictionary.

	In \cite{yang2003accelerating}, clustering, offline recognition, first comparing input to centroid character,
	therafter search within.

@@

	``A linear--time elastic matching algorithm for on--line recognition of handwritten Japanese characters'' (Nakagawa)
	presents the LTM--algorithm, an alternative and attractive way of extracting feature points.

@@

@@

	\begin{figure}
		\centering
		\includegraphics[width=2.75in]{./fig/experimental-implementation.eps}
		\caption{Experimental implementation. The input is first analyzed by the coarse classifier, resulting in the $<GHA\ldots>$ feature representation.
		Thereafter, the routing network selects which cluster to search in, and the image data is passed to the corresponding CANN for fine--grain classification.}
		\label{fig_experimental_implementation}
	\end{figure}

@@

	Total strokes: 78785

>>>>

	This paper documents a work in progress on the topic of intelligent handwriting recognition of Japanese characters.
	The remainder of the article is structured as follows:
	In section \ref{sec:problem_description} we present the Japanese writing system and outline the primary issues with handwriting recognition for asian script;
	thereafter in \ref{sec:previous_work}, we discuss some notable advances aimed at solving various aspects of the aforementioned problems.
	An explanation of our solution approach is given in section \ref{sec:proposed_solution}, and an initial, experimental implementation is described in \ref{sec:experiments}
	-- the results of which are recorded and examined in section \ref{sec:experiment_results}. Finally, conclusions and future work is presented in sections
	\ref{sec:conclusions} and \ref{sec:future_work}, respectively.

	\begin{figure}
		\centering
		\includegraphics[width=2.75in]{./fig/yama-ryuu-kane.eps}
		\caption{Sample characters. The kanji ``yama'' (mountain), ``ry\=u'' (dragon), and ``kane'' (bell), written with 3, 10, and 20 strokes, respectively.}
		\label{fig_kanji_sample}
	\end{figure}

	\vfill

@@

	Any form of digital handwriting recognition is a complex undertaking,
	where the performance of the system is impacted by a multitude of factors -- spanning
	everything from the quality and quantity of training data, to resilience toward input
	translation, rotation, and noise. As the number of candidate categories increase
	the size of the search space, however, the task quickly grows monumental.

@@

	Given that the category search space for Japanese characters is an order of magnitude larger and contains a vastly differing set of
	characteristics than its western counterparts, the same designs that yield highly accurate results on 
	western handwriting recognition tasks will not perform satisfactory when applied to asian script \cite{jager2003state, tappert1990state, liu2004online}
	-- unless the solution relies on complex and computationally expensive techniques, such as  ``deep'' neural networks. \cite{ciresan2012multi}

	In continuation, we describe a flexble, modular design scheme that splits the identification task into coarse and fine steps,
	thereby reducing the complexity of each undertaking. The design scheme also permits replacing the segmentation and classification strategies,
	and facilitates the parallelization of the fine classification components.

	\begin{figure}
		\centering
		\begin{tikzpicture}[font=\small]
			\begin{axis}[
				ycomb,
				xlabel={Number of strokes},
				ylabel={Number of characters},
			]
				%\addplot[fill=white] coordinates {
				\addplot [] coordinates {
					(1, 6)
					(2, 32)
					(3, 64)
					(4, 115)
					(5, 151)
					(6, 199)
					(7, 318)
					(8, 434)
					(9, 473)
					(10, 544)
					(11, 581)
					(12, 581)
					(13, 532)
					(14, 435)
					(15, 434)
					(16, 369)
					(17, 299)
					(18, 207)
					(19, 175)
					(20, 135)
					(21, 106)
					(22, 69)
					(23, 49)
					(24, 37)
					(25, 20)
					(26, 12)
					(27, 8)
					(28, 6)
					(29, 3)
					(30, 2)
				};
			\end{axis}
		\end{tikzpicture}
		\caption{Distribution of 6,400 kanji by number of stroke. Min = 2, Max = 581. \emph{Data source: KanjiVG.} \cite{kanjivg}}
		\label{fig_kanji_stroke_hist}
	\end{figure}

@@

	A vast body of work has been amassed on the topic of Japanese handwriting recognition.
	Here we summarize some notable publications that influenced our adopted approach.

	In \cite{joe1989large}, Mori and Joe present ``selective'' and ``integrative'' neural networks that 
	segment categories into small groups, thereby improving the recognition rate of each network.

	% Took A-H classification from here
	In \cite{nakai2001substroke}, the authors adapt a continuous speech recognition algorithm utilizing
	hidden Markov models for the purpose of online kanji recognition. Captured strokes are segmented into
	substrokes and classified according to directionality (see figure \ref{fig_stroke_categories}),
	and these characteristics are in turn employed as dictionary search keys.

	After structuring the search space by clustering, Yang et. al. perform two--stepped offline recognition by first
	comparing the input character to the centroids of each cluster, and then distinguishing between the members of the cluster
	whose centroid most closely matched the input. \cite{yang2003accelerating},

	In \emph{Hybrid pen-input character recognition system based on integration of online-offline recognition},
	the authors integrate online and offline recognition strategies, leveraging the advantages of each technique.
	In addition to a discussion of various integration techniques, two feature extraction methods are described: 
	a gradient--based technique for offline input, and a recursive substroke extractor for online input.

@@

@@

	\begin{figure}
		\centering
		\includegraphics[width=1.75in]{./fig/stroke-categories.eps}
		\caption{A stroke may be classified according to its directionality.
			Further classes may be used to differentiate between long and short strokes,
		or to accomodate for ``pen--up'' motions. Here, the strokes of the kanji ``ki'' (tree) are identified as A-G-F-H.}
		\label{fig_stroke_categories}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=2.75in]{./fig/experimental-implementation.eps}
		\caption{Experimental implementation. The input is first analyzed by the coarse classifier, resulting in the G-H-A\ldots feature representation.
		Thereafter, the routing network selects which cluster to search in, and the image data is passed to the corresponding CANN for fine--grain classification.}
		\label{fig_experimental_implementation}
	\end{figure}

@@
